---
title: "Processing"
---

```{r setup, include=FALSE}

# Do not echo code chunks in rendered document

knitr::opts_chunk$set(echo = FALSE);

# Do not render values returned by code in code chunks

knitr::opts_chunk$set(results = "hide")

# Clear the global environment

rm(list = ls());

# Create an environment to hold metadata to be transferred to later scripts

metaEnv <- new.env();

```

<!-- Automatically populate a description of the compilation of this file. -->

Generated from R markdown file **./02_protocol/`r knitr::current_input()`**, last compiled on `r Sys.time()`

```{r}

# Make sure target directories exist.

tempPath <- "./03_incremental/temp";
dir.create(
  path = tempPath,
  recursive = TRUE,
  showWarnings = FALSE
);
productPath <- "./04_product";
dir.create(
  path = productPath,
  recursive = TRUE,
  showWarnings = FALSE
);

# Read the project attributes table
# and restructure for convenience.

atts <- as.data.frame(
  t(as.matrix(
    readxl::read_excel(
      path = "./01_input/meta/attributes.xlsx",
      sheet = "attributes",
      range = readxl::cell_limits(ul = c(2, 3)),
      col_names = TRUE,
      col_types = rep("text", times = 10)
    )
  ))
);
names(atts) <- readxl::read_excel(
  path = "./01_input/meta/attributes.xlsx",
  sheet = "attributes",
  range = readxl::cell_limits(ul = c(3, 2), lr = c(NA, 2)),
  col_names = "rownames",
  col_types = "text"
)$rownames;
atts[is.na(atts)] <- "";

# Specify the range of scale for time axes on plots

xmin <- as.POSIXct("2017-09-28");
xmax <- as.POSIXct("2018-11-02");

```

## Load Annual Aggregate NH4 SRP data table

```{r}

# Specify the column names of the files being read

col.names = c(
  "rowNumber",
  "project",
  "dateString",
  "day",
  "month",
  "year",
  "siteID",
  "rep",
  "NH4N",
  "SRP",
  "NO3"
);

# Read data from input file(s)

table <- read.table(
    file = "./03_incremental/00c-202206-validationQAQC/AnnualAggregateFile-NH4-SRP-NO3-WY2018.csv",
    sep = ",",
    skip = 1,
    header = FALSE,
    col.names = col.names
);

```

Read a total of `r nrow(table)` records for the NH4 SRP NO3 data table.


## Adjust NH4 SRP NO3 table and define column metadata

Reformat the date string to YYYYmmdd. Reformat the site ID for clear matches with standard with leading zeroes. Remove unnecessary fields.

```{r}

# Define the table of metadata for the table

metaEnv$tableNH4SRP.meta <- data.frame(
  dateString = atts$date,
  year = atts$year,
  month = atts$month,
  day = atts$day,
  siteID = atts$siteID,
  rep = atts$rep,
  NH4N = atts$NH4N,
  SRP = atts$SRP,
  NO3 = atts$NO3,
  row.names = rownames(atts)
);

# Filter columns for data product table

table <- table[, names(metaEnv$tableNH4SRP.meta)];

# Specify table name and description

metaEnv$tableNH4SRP.name <- "AnnualAggregateFile-NH4-SRP-NO3-WY2018";
metaEnv$tableNH4SRP.desc <- paste(
  "Surface water samples are collected from thirteen sites ",
  "along the mainstem of the Upper Clark Fork River. ",
  #"and three sites from major tributaries to the Upper Clark Fork River ",
  #"including the Little Blackfoot, Flint Creek, and Rock Creek. ",
  "Water samples are collected at each monitoring site in triplicate ",
  "and filtered with a 0.7 µm glass fiber filter. Nutrient samples ",
  "are analyzed using a spectrophotometric flow injection analyzer for nitrate (N-NO3), ",
  "soluble reactive phosphorus ((SRP) P-PO4), and ammonium (N-NH4) concentrations."
);

# Create a numerical dates to determine earliest and latest dates for metadata

dates <- as.POSIXct(table$dateString, format = "%Y-%m-%dT%H:%M:%SZ", tz = "");
metaEnv$startTime <- min(dates);
metaEnv$endTime <- max(dates);

# Reformat date string and siteID

table$dateString <- format(dates, format = "%Y%m%d");
table$siteID <- sprintf(fmt = "%03d", table$siteID);

# Update metadata site list with all sites with data in this table.

sites <- sort(unique(table$siteID));
metaEnv$sites <- sites;

```

`r sprintf("**%s.csv**", metaEnv$tableNH4SRP.name)`: `r metaEnv$tableNH4SRP.desc`

`r knitr::kable(x = metaEnv$tableNH4SRP.meta) `

```{r}

# Write the data table to the product

write.csv(
  x = table,
  file = sprintf(
    "%s/%s.csv",
    productPath,
    metaEnv$tableNH4SRP.name
  ),
  row.names = FALSE
)

# Open a PDF device to render the data visualization

pdf(
  file = sprintf(
    "%s/%s_vis.pdf", 
    productPath,
    metaEnv$tableNH4SRP.name
  ),
  width = 12,
  height = 8
);

  # Set the canvas margins around the graphing area

  par(
    mar = c(4.2, 4.5, 1, 1)
  )
  
  # Plot the data with a monthly abscissa
  
  plot(
    x = dates,
    xlab = "Time",
    xaxt = "n",
    xlim = c(xmin, xmax),
    y = table$NH4N,
    ylab = bquote(
        .("[")* NH[4]^+{}* .("]") ~ .("(") ~mg ~N~ L^{-1} ~ .(")")
    ),

    col = 1:length(sites)
  );
  axis.POSIXct(
    side = 1,
    at = seq.POSIXt(
      from = xmin,
      to = xmax,
      by = "months"
    ),
    format = "%Y %b"
  )
  
  # Render the legend with the site colors
  
  legend(
    x = "topleft",
    bty = "n",
    legend = sites,
    pch = 1,
    col = 1:length(sites),
    title = "Site ID"
  )

   # Plot the data with a monthly abscissa
  
  plot(
    x = dates,
    xlab = "Time",
    xaxt = "n",
    xlim = c(xmin, xmax),
    y = table$SRP,
    ylab = bquote(
        .("[")* SRP* .("]") ~ .("(") ~mg ~P~ L^{-1} ~ .(")")
    ),
    col = 1:length(sites)
  );
  axis.POSIXct(
    side = 1,
    at = seq.POSIXt(
      from = xmin,
      to = xmax,
      by = "months"
    ),
    format = "%Y %b"
  )
  
  # Render the legend with the site colors
  
  legend(
    x = "topleft",
    bty = "n",
    legend = sites,
    pch = 1,
    col = 1:length(sites),
    title = "Site ID"
  )

# Close the device to write the PDF file
  
dev.off();

```

Data table written to `r sprintf("./%s.csv", metaEnv$tableNH4SRP.name) `


## Write metdata object

```{r}

# Specify the path to the temporary metadata file and write
# the metadata environment to it

file <- sprintf(
  "%s/metadata.RData",
  tempPath
);
saveRDS(
  object = metaEnv,
  file = file
)

```

Temporary metadata file written to `r file `


## Summary of R session used to compile this Rmarkdown

```{r results = "markup"}

# Render the session information

print(sessionInfo()) 

```
